---
title: "Visualization for IBM Survey"
author: "Nikky Xiong"
date: "Feb 6, 2020"
output: html_document
---

```{r global options,echo=F}
set.seed(1:7)
library(knitr)
opts_chunk$set(warning = F,message = F,error = F)
```

```{r, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(tidytext)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
```

#### data summary 

```{r}
df <- readr::read_csv('complaints.csv')
df %>% summary()
df <- df %>% head(500)
```

#### text cleaning function

```{r}
clean_text <- function(variable){
    
    text = tibble(txt = variable)
    
    text <- text %>% 
    unnest_tokens(word, txt) %>% 
    anti_join(stop_words) %>%   
    na.omit() %>% 
    count(word, sort = TRUE)
    
    return(text)
}
```

#### text cleaning by variables

```{r, message=FALSE, warning=FALSE}
product <- clean_text(df$Product)
issue <- clean_text(df$Issue)
complaints <- clean_text(df$`Consumer complaint narrative`)
response <- clean_text(df$`Company public response`)
```

#### visualization

```{r}
wordcloud(words = product$word, freq = product$n, 
          colors=brewer.pal(6, "Dark2"), min.freq = 1)
```

___`Credit` is the most important and the most frequently mentioned key words in the products. `Consumer`, `reports`, `perosnl`, `repair`, and `services` are also worth paying attention to.___


```{r}
wordcloud(words = issue$word, freq = issue$n, 
          colors=brewer.pal(6, "Dark2"), min.freq = 1)
```

___`Report[ing] incorrect information` seems to be the most important and the most frequently mentioned key words in the issues.___
